### 2018-07-16 pilot_manuscript.Rmd
Some things added here and there

```{r load_packages, include = FALSE}
library("papaja")
library(MuMIn)
```
# Introduction
Talk about MFT, MFQ, MFD
Talk about political discourse, nature of news media in 2018/Trump era
This project brings the two together in holy matrimony.
# Method

@@

```{r mlm table}
##three models
table = matrix(NA, nrow = 5, ncol = 10)
colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")

@@

# Results
Anymore screening/data prep here?

@@

Comparisons between the models can be found in Table 1. 
# Discussion
How it turned out
What to do for future project
Argue: why is still a good thing to study??

>>>>

```{r load_packages, include = FALSE}
library("papaja") #R says this package doesn't exist in current version :/
library(MuMIn)
```
# Introduction
Talk about MFT, MFQ, MFD (primer on moral psychology?)

(Brief) primer on political research?

Talk about political discourse, nature of news media in 2018/Trump era

This project brings the two together in holy matrimony.
# Method

@@

```{r mlm table}
##three models
table = matrix(NA, nrow = 5, ncol = 10)

##ARE ALL OF THESE COLUMNS NEEDED?? ALSO, ORDER?
colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")

@@

# Results
Any more screening/data prep here?

@@

Comparisons between the models can be found in Table 1. 
# Discussion
How it turned out

Limitations of this one (no rationale behind choosing sources except "people say NPR's liberal??")

What to do for future project (focus on one MF? Different sources? More sources?)

Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, "alternative facts," subjective reality - philosophical stuff)
